---
title: "2025 Revenue Forecast for Top 12 German Companies"
author: "Rani"
date: "2024-12-24"
output:  pdf_document

---

```{r Load necessary libraries, include=FALSE}
# Load the necessary libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
library(scales)
library(furrr) 
library(future)
```


```{r Load dataset, include=FALSE}
# Load your dataset (make sure the file path is correct)
df <- read.csv('C:/Users/acer/Documents/R_Case_Studies/FinPrediction/Top_12_German_Companies.csv')
```

## Inspect dataset

```{r Inspect dataset, echo=FALSE}
# Inspect the column names
colnames(df)
```


```{r Rename for model, include=FALSE}
# Temporary rename for fitting the model
df_temp <- df %>%
  rename(ds = Period, y = Revenue)
```


```{r Check for missing values, include=FALSE}
# Check for missing values in the y column
missing_values <- sum(is.na(df_temp$y))
print(paste("Number of missing values in Revenue:", missing_values))
```

```{r Remove rows with NA values, include=FALSE}
# Handle missing values (e.g., remove rows with NA values)
df_temp <- df_temp %>%
  filter(!is.na(y))
```


```{r Remove infinite values, include=FALSE}
# Check for infinite values and remove them
infinite_values <- sum(is.infinite(df_temp$y))
print(paste("Number of infinite values in Revenue:", infinite_values))
df_temp <- df_temp %>%
  filter(!is.infinite(y))
```

```{r Remove zero values, include=FALSE}
# Check for zero values and remove them if necessary
zero_values <- sum(df_temp$y == 0)
print(paste("Number of zero values in Revenue:", zero_values))
df_temp <- df_temp %>%
  filter(y != 0)
```
```{r Final check after cleaning, include=FALSE}
# Final check after cleaning 
print("Data after cleaning:") 
print(summary(df_temp$y))
```
```{r Check Dataframe, echo=FALSE}
head(df)
```


```{r Prepare dataset for predictions, include=FALSE}

# Convert Period to Date type with the correct format and handle NAs
df <- df %>%
  mutate(Period = as.Date(Period, format="%m/%d/%Y")) %>% 
  filter(!is.na(Period))

# Check the format of the dates
print(head(df$Period))

# Extract Year from Period
df <- df %>%
  mutate(Year = year(Period))
```
## Summarized Yearly Revenue

```{r Summarize yearly Revenue, echo=FALSE}
# Summarize Revenue Yearly per Company
yearly_revenue <- df %>%
  group_by(Company, Year) %>%
  summarize(Total_Revenue = sum(Revenue, na.rm = TRUE), .groups = 'drop')

# Adjust y-axis limits with padding
y_max <- max(yearly_revenue$Total_Revenue, na.rm = TRUE) * 1.1  # Adding 10% padding to the top

# Scatter Plot of Yearly Revenue per Company
ggplot(yearly_revenue, aes(x=Year, y=Total_Revenue, color=Company)) +
  geom_point(size=3) +
  labs(title="Yearly Revenue per Company", x="Year", y="Total Revenue") +
  scale_y_continuous(labels = comma, expand = c(0, 0), limits = c(0, y_max)) +  # Display real values for y and add padding to the top
  theme_minimal() +
  # Remove company names from x-axis
  theme(axis.title.y = element_blank(), axis.title.x =element_blank())
```

```{r Yearly Revenue Tibble, echo=FALSE}
# Print the yearly_revenue data frame with comma formatting 

yearly_revenue <- yearly_revenue %>% mutate(Total_Revenue = comma(Total_Revenue)) 
print(yearly_revenue, n = Inf)
```

## Observations: 

Most companies exhibited resilience and stability during the pandemic years (2020-2023), with minor fluctuations in revenue.

Companies in the healthcare and telecommunications sectors showed strong performance:

* Merck KGaA
* Deutsche Telekom AG
* Bayer AG

This is a reflection of the companies' increased demand for their services during the pandemic.

Automotive companies, such as Daimler AG, BMW AG, and Volkswagen AG, faced challenges but managed to adapt and stabilize their revenues.

## Average Yearly Revenue Per Company

```{r Average Yearly Revennue Per Company, echo=FALSE}
# Filter data from 2017 to 2024
df <- df %>%
  filter(Year >= 2017 & Year <= 2024)

# Summarize average Revenue per Company from 2017 to 2024 and arrange by highest average revenue
average_revenue <- df %>%
  group_by(Company) %>%
  summarize(Average_Revenue = mean(Revenue, na.rm = TRUE)) %>%
  arrange(desc(Average_Revenue))

# Print the average revenue with comma formatting
average_revenue <- average_revenue %>%
  mutate(Average_Revenue = scales::comma(Average_Revenue))

print(average_revenue)
```
# Profitability Analysis

```{r Revenue Growth Analysis, echo=FALSE}
# Summarize average Net Income per Company from 2017 to 2024
average_net_income <- df %>%
  filter(Year >= 2017 & Year <= 2024) %>%
  group_by(Company) %>%
  summarize(Average_Net_Income = mean(Net_Income, na.rm = TRUE)) %>%
  arrange(desc(Average_Net_Income))

# Calculate Net Income Margin (Net Income / Revenue) and average it
net_income_margin <- df %>%
  filter(Year >= 2017 & Year <= 2024) %>%
  group_by(Company) %>%
  summarize(Average_Net_Income_Margin = mean(Net_Income / Revenue, na.rm = TRUE)) %>%
  arrange(desc(Average_Net_Income_Margin))

# Print the results with comma formatting
average_net_income <- average_net_income %>%
  mutate(Average_Net_Income = scales::comma(Average_Net_Income))

net_income_margin <- net_income_margin %>%
  mutate(Average_Net_Income_Margin = scales::percent(Average_Net_Income_Margin))

print(net_income_margin)
```

## Average Net Income Margin Per Company

```{r Average Net Income Margin Per Company, echo=FALSE}
# Ensure 'Average_Net_Income_Margin' is numeric
net_income_margin <- net_income_margin %>%
  mutate(Average_Net_Income_Margin = as.numeric(gsub("%", "", Average_Net_Income_Margin)) / 100)

# Plot the average Net Income Margin
ggplot(net_income_margin, aes(x = reorder(Company, -Average_Net_Income_Margin), y = Average_Net_Income_Margin, fill = Company)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent) +  # Ensure percentage y-axis labels
  labs(title = "Average Net Income Margin (2017-2024) by Company",
       x = "Company",
       y = "Net Income Margin",
       fill = "Company") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(),
        axis.title.y = element_blank())  # Hide y-axis label

```
## Observations: 

* Allianz SE stands out as the top performer in terms of net income margin, indicating strong profitability.

* The other companies have relatively similar margins, showing consistent and stable performance

## Predicted 2025 Revenue

```{r Predicted 2025 Revenue, echo=FALSE}
# Filter data from 2017 to 2024
yearly_revenue <- df %>%
  filter(Year >= 2017 & Year <= 2024) %>%
  group_by(Company, Year) %>%
  summarize(Total_Revenue = sum(Revenue, na.rm = TRUE), .groups = 'drop')

# Ensure there are no NA/NaN/Inf values in Total_Revenue
yearly_revenue <- yearly_revenue %>%
  filter(is.finite(Total_Revenue))

# Fit a linear regression model for each company and predict revenue for 2025
predicted_revenue <- yearly_revenue %>%
  group_by(Company) %>%
  do({
    model <- lm(Total_Revenue ~ Year, data = .)
    predicted_revenue_2025 <- predict(model, newdata = data.frame(Year = 2025))
    data.frame(Predicted_Revenue_2025 = predicted_revenue_2025)
  }) %>%
  ungroup()

# Print the predicted revenue for 2025 with comma formatting
predicted_revenue <- predicted_revenue %>%
  mutate(Predicted_Revenue_2025 = scales::comma(Predicted_Revenue_2025))

print(predicted_revenue)
```

## Bar Graph of Predicted Revenue for 2025

```{r Visualization Predicted Revenue, echo=FALSE}

# Ensure 'Predicted_Revenue_2025' is numeric
predicted_revenue <- predicted_revenue %>%
  mutate(Predicted_Revenue_2025 = as.numeric(gsub(",", "", Predicted_Revenue_2025)))

# Plot the predicted 2025 revenue
ggplot(predicted_revenue, aes(x = reorder(Company, -Predicted_Revenue_2025), y = Predicted_Revenue_2025, fill = Company)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::comma) +  # Ensure exact y-axis labels
  labs(title = "Predicted Revenue for 2025 by Company",
       fill = "Company") +  # Remove y-axis label
  theme_minimal() +  # Remove company names from x-axis
  theme(axis.title.x = element_blank(), axis.text.x = element_blank(), 
       axis.title.y = element_blank())
```
## Analysis

### Top Performers:

* Allianz SE, BASF SE, and Bayer AG is seen to have stronger market positions in the year ahead. 

### Mid-Range Performers:

* BMW AG
* Daimler AG
* Deutsche Telekom AG
* Merck KGaA
* Siemens AG

### Lower Performers:

* Deutsche Bank AG, Porsche AG, and SAP SE have lower predicted revenues compared to other companies. 

* This could indicate either a more niche market focus or challenges in revenue growth.

### Bayer AG
* It has the lowest predicted revenue among the top companies although the it is still significant. This suggests that with its strong brand presence and market reach, it will be able to face challenges despite competition.